Spin canonical divisors of log stacky curves

### 2015-06-19 stacky_write_up/spin_cring.tex
added third admissible condition

\newcommand \trdeg{\text{tr. deg }}
\newcommand \codim{\text{codim}}
\newcommand \rk{\text{rk }}
\newcommand \di{\text{div }}
\newcommand \depth{\text{depth }}
\DeclareMathOperator{\ord}{ord}
\newcommand \halfcan{L}

%%%%%%%%%%%%%%%%%%% spin cring custom commands %%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. \todo{Rewrite this to be more precise}
\end{thm}
\begin{proof}

@@

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
Suppose $\delta=\deg(\halfcan)>0$.  Then we can explicitly write out $D=K_\sx+\Delta=K_X+\sum \subhalf{i}$   Let us consider $\delta \geq 2$.

@@

In this section, we will prove that if $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. This is proven in Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather involved induction. In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.

@@

\begin{lem}
\label{sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $\halfcan = \subhalf i$. There are generators $y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$. \todo{Include the order} 
Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively. \todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, l oetting $x_j$ range over all $x$ variables
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y_3,\ldots, y_e,z_4,z_5] + \\
	\langle y_i y_j \mid 1 \leq i < j-3 \leq e \rangle +\\
	\langle y_i x_j \mid i > 3 \rangle +\\
	\langle z_i y_j \mid j > 3 \rangle  +\\
	\langle z_i x_j \mid 4 \leq i \leq 5\rangle + \\
	\langle z_iz_k \mid 4 \leq i \leq j \leq 5 \rangle 
\end{align*}

@@

\ssec{Inductive theorem: Increasing the Ramification Orders}
\label{ssec:g_0_ram_orders}
In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}. Under fairly general conditions, this theorem will show that if

\begin{defn}
\label{defn:admissible}
A pair $(\sx',e_i')$, with point $P$ corresponding to $e-2$ is admissible if
\begin{enumerate}
	\item There is an element $y_{e-2} \in R'$ so that $R'$ admits a presentation $(k[x] \otimes k[y_{e-2}])/I'$ with $\deg y_{e-2} = e-2$ and $-ord_P(y_{e-2}) = \frac{e-3}{2}$.
\item For all $z \neq y_{e-2}$ generators of $R'$ we have
\begin{align*}
	\frac{- ord_P(z)}{\deg z} < \frac{e-3}{2(e-2)}
\end{align*}
\item We have
\begin{align*}
	\deg \lfloor e K_{\sx'} \rfloor \geq 0
\end{align*}
\end{enumerate}
\end{defn}

>>>>

\newcommand \trdeg{\text{tr. deg }}
\newcommand \codim{\text{codim}}
\newcommand \rk{\text{rk }}
\newcommand \di{\text{div }}
\newcommand \depth{\text{depth }}
\DeclareMathOperator{\ord}{ord}

@@

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. \todo{Rewrite this to be more precise}
\end{thm}
\begin{proof}

@@

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
Let us consider $\delta \geq 2$.

@@

In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. This is proven in Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather involved induction. In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.

@@

\begin{lem}
\label{sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  log stacky curves $R \subset R'$ be the corresponding inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf i$. There are generators $y_3,y_4,y_5$ of $R_{D+D'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$. \todo{Include the order}
Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively. \todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y_3,\ldots, y_e,z_4,z_5] + \\
	\langle y_i y_j \mid 1 \leq i < j-3 \leq e \rangle +\\
	\langle y_i x_j \mid i > 3 \rangle +\\
	\langle z_i y_j \mid j > 3 \rangle  +\\
	\langle z_i x_j \mid 4 \leq i \leq 5\rangle + \\
	\langle z_iz_k \mid 4 \leq i \leq j \leq 5 \rangle 
\end{align*}

@@

\ssec{Inductive theorem: Increasing the Ramification Orders}
\label{ssec:g_0_ram_orders}
In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}. Under fairly general conditions, this theorem will allow us to show that if Theorem ~\ref{thm:ramification_order_induction} holds for a curve with signature $(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.

\begin{defn}
\label{defn:admissible}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves, ramified over $Q_1,\ldots, Q_r$ and let $J \subset \{1,
\ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
$$
\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}$$
Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$, {\bf admissible} if the following three conditions hold.
\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} \in R'$ so that $R'$ admits a presentation
\begin{align*}
	R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}
so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a generator of $R'$ we have
\begin{align*}
	\frac{- ord_{Q_i}(z)}{\deg z} < \frac{e_i'-1}{2(e_i')}.
\end{align*}
\item[(Ad-iii)] For all $i \in J$ we have
\begin{align*}
	\deg \lfloor e K_{\sx'} \rfloor \geq \eta(i)
\end{align*}
where
\begin{align*}
	\eta(i) = \#\{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
\end{align*}
\end{enumerate}
\end{defn}
